A user-extensible and adaptable parser architecture

### 2008-05-30 papers/sgai-2008/paper.tex
Mention that actions can return a modified input line to be parsed again.

XXX MAYBE MENTION THAT LOG LINES COULD BE MODIFIED AND RE-PARSED\@?  MAYBE
WORK IT INTO THE ARCHITECTURE CHARACTERISTICS SECTION, AND ELSEWHERE\@.

@@

@@

    \item [Partially context-sensitive actions:]  XXX IS THIS THE CORRECT
        TERMINOLOGY\@?  Actions can consult the results (or lack of
        results) of previous actions when executing, providing some context
        sensitivity.  Actions can not inspect past or upcoming inputs.

>>>>

@@

Actions may also return a modified input line which will be parsed as if
read from the input stream, allowing for cascaded parsing XXX REFERENCE\@.
This is a powerful facility allowing a generic rule and action to parse
part of the input, followed by more specific rules and actions parsing the
remainder.

@@

    \item [Partially context-sensitive actions:]  XXX IS THIS THE CORRECT
        TERMINOLOGY\@?  Actions can consult the results (or lack of
        results) of previous actions when executing, providing some context
        sensitivity.  Actions can not inspect past or upcoming inputs,
        however allowing actions can return a modified input line that will
        be parsed as if read from the input stream, allowing for cascaded
        parsing XXX REFERENCE\@.
